## Essential Packages: dplyr {.packages-dplyr}

`r htmltools::includeCSS("./slide.css")`

`r htmltools::div(
    id = "packages-dplyr-left",
    htmltools::p(
        class = "packages-dplyr-em",
        "Grammar for Data Manipulation"
    ),
    htmltools::div(
        id = "packages-dplyr-left-1",
        htmltools::img(
            id = "packages-dplyr-left-1-table",
            src = knitr::image_uri("../../img/data-table.png")
        )
    ),
    htmltools::div(
        id = "packages-dplyr-left-2",
        htmltools::img(
            id = "packages-dplyr-left-2-table",
            src = knitr::image_uri("../../img/data-table.png")
        )
    ),
    htmltools::div(
        id = "packages-dplyr-left-3",
        htmltools::img(
            id = "packages-dplyr-left-3-table",
            src = knitr::image_uri("../../img/data-table.png")
        )
    )
)`

<div id = "packages-dplyr-right">
```{r, comment=NA, eval=FALSE}
library(dplyr)
mtcars %>% 
    filter(mpg >= 15) %>% 
    group_by(cyl) %>% 
    summarise(numCARS = n(),
              avgMPG = mean(mpg),
              avgHP = mean(hp),
              medWT = median(wt),
              pctMANUAL = mean(am)) %>% 
    arrange(cyl)
```
```{r, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
```
```{r, comment=NA, echo=FALSE}
mtcars %>% 
    filter(mpg >= 15) %>% 
    group_by(cyl) %>% 
    summarise(numCARS = n(),
              avgMPG = mean(mpg),
              avgHP = mean(hp),
              medWT = median(wt),
              pctMANUAL = mean(am)) %>% 
    arrange(cyl)
```
<a href="https://github.com/hadley/dplyr">https://github.com/hadley/dplyr</a>
</div>
