## Package Functions {.package-functions}

`r htmltools::includeCSS("./slide.css")`

<div class = "build">

<div id = "package-functions-left">

<p class = "package-functions-emy">Don't reinvent the wheel!</p>

<p class = "package-functions-emb">R is highly extensible through packages</p>

Many amazing packages come installed with R. See the **Packages** pane in RStudio or run the following command in the R console: `installed.packages()`

To access the functions (*and other objects*) from a package, first load the package using the `library()` function.

</div>

<div id = "package-functions-right">

```{r, eval=FALSE}
qplot(x = Petal.Width, y = Petal.Length, data = iris)
```

<pre><code id = "package-functions-error">Error: could not find function "qplot"</code></pre>

```{r, fig.width=5, fig.height=3.5}
library(ggplot2)
qplot(x = Petal.Width, y = Petal.Length, data = iris)
```

</div>

<div id = "package-functions-left-bottom">>
<p class = "package-functions-left-dblcolon">\* Can also use the double-colon operator, for example: <span><code id = "package-functions-left-dblcolon">ggplot2::qplot()</code></span></p>

</div>

</div>
